It still seems that black has hope in these extremely unfair variants of chess

### 2014-03-10 chesstego/paper.tex
Sync for mtv trip

Lo! This version is finally satisfactory. White shall pick one of her
safe pieces (e.g., one of the rooks) as Flag, and choose Black's b7~pawn
as Black~Flag. White's winning move is c2c4 and then Qb3, with Black~Flag
unable to escape the B file. Choosing the f7~pawn works as well.

@@

% Chessy Crush Saga

@@

>>>>

Lo! This version is finally satisfactory. In this version we need not
equivocate over who shall win. White picks one of her very safe pieces
(e.g., one of the rooks) as Flag, and chooses Black's b7~pawn as
Black~Flag. White's winning move is c2c4 and then Qb3, with Black~Flag
unable to escape the B file. Choosing the f7~pawn works as well.

@@

@@

\section{Chess Who?}

The board game {\em Guess Who?} disappointed millions of children with
its delightful television commercial that far outstripped the
capabilities of the actual game. This required them to add a
disclaimer to the commercial, ``Game cards do not actually talk.'' In
{\em Guess Who?}, players take turns trying to guess the identity of
the opponent, among a fixed set of personalities with traits like
curly hair, straight hair, brown hair, short hair, bangs, long hair,
blonde hair, red hair, or glasses. One player asks, ``Do you have
curly hair?'' and the other says ``Yes'' or ``No'' and then the first
player can eliminate all the remaining personalities that don't have
the trait. It's basically binary search, but for kids.

In {\em Chess Who?}, which is the chess version, players have two
different options on each turn. They can either move a piece like
normal, or ask a question of their opponent. The question must be
about the physical characteristics of the pieces, for example, ``Does
your piece have curly hair?'' No pieces have curly hair, so nothing
happens. The opponent might ask a different question, on the next turn,
like ``Does your piece have straight hair?'' No pieces have straight
hair, so nothing happens. On the next turn, suppose the player asks,
``Does your piece have brown hair?'' No pieces have brown hair,
nor any hair at all, and no pieces have any brown parts at all either.
Stop asking. Next, Black asks, ``Does your piece have crennelations?''
Both of White's rooks have crennelations, so they are eliminated from
the board (Figure~\ref{fig:crennelations}).

\begin{figure}[ht]
\begin{center}
\chessboard[
   setfen=rnbqkbnr/pppppppp/8/8/8/8/PPPPPPPP/1NBQKBN1]
\end{center}\vspace{-0.1in}
\caption{
  The board after
  1. Does your piece have curly hair?
     \ldots Does your piece have straight hair?
  2. Does your piece have brown hair?
     \ldots Does your piece have crennelations?
}
\label{fig:crennelations}
\end{figure}

Next, White might ask, ``Does your piece have a cross on his hat?''
This matches both Bishops and the King, but Black responds ``Check!''
because it is illegal to ask a question that would eliminate the King.

This variation produces draws easily. An example Nash Equilibrium:
White begins by asking, ``Does your piece have three lobes like a
truncated snowman, {\em or} crennelations, {\em or} horse ears, {\em
  or} two weird long shoulder-ribbons that I don't know what they are,
{\em or} five pointy tines on her crown?'' This matches all of Black's
pieces except his king, so he removes them all. But then Black asks:
``Does your piece {\em not} have a lumpy crown?'' which matches all of
White's pieces except his king. So all we have left is the two kings,
which is known to be a draw~\cite{pawnless}.

% Chessy Crush Saga
% Battleship + Chess = Battlechess
% Chess Tac Toe
% Chesslers of Catan
% Chesstris
% Hungry Hungry Hipposchess

% Monopoly?
